\Large \bf Dark Decoys: Conjuring Proxies from Unused Address Space

### 2019-02-15 paper/figures.tex
binomial, not normal distribution
Add bandwidth fig

\newcommand{\FigIpBits}{
\begin{figure}[t]
    \centering
    \vspace{-0.5in}
    \includegraphics[width=\linewidth,clip]{figures/ip-bits-set-pdf.pdf}
    \caption{\textbf{IPv6 Entropy}---%
        We observed 30 minutes of IPv6 traffic on our tap to the /32 of the ISP's network.
        In each address observed, we counted the number of bits set, and compared this to
        randomly generated addresses. If the 96 non-network bits
        of each address were chosen randomly, we would expect to see a normal distribution
        (shown as Random). In practice, the distribution of observed IP addresses has much fewer
        bits set, suggesting that censors might be able to distinguish between dark decoy addresses
        and legitimate ones.
        %We note there are several /64 subnets that had many
        %addresses that appeared random (visibly overlapping the random distribution).
    }
    \label{fig:ipbits}
\end{figure}
}

>>>>

\newcommand{\FigTapBandwidth}{
\begin{figure*}[t]
    \centering
    \includegraphics[width=0.90\linewidth,clip]{figures/decoy-tap-bandwidth.png}
    \caption{\textbf{Tap Bandwidth}\,---\, %
        We deployed our \scheme implementation in a realistic ISP testbed on a
        (full duplex) tap of a 10~Gbps router. As shown in a typical week, traffic
        ranges from 2-17~Gbps.
    }
    \label{fig:tap-bandwidth}
\end{figure*}
}

\newcommand{\FigIpBits}{
\begin{figure}[t]
    \centering
    \vspace{-0.5in}
    \includegraphics[width=\linewidth,clip]{figures/ip-bits-set-pdf.pdf}
    \caption{\textbf{IPv6 Entropy}---%
        We observed 30 minutes of IPv6 traffic on our tap to the /32 of the ISP's network.
        In each address observed, we counted the number of bits set, and compared this to
        randomly generated addresses. If the 96 non-network bits
        of each address were chosen randomly, we would expect to see a Binomial distribution
        (shown as Random). In practice, the distribution of observed IP addresses has much fewer
        bits set, suggesting that censors might be able to distinguish between dark decoy addresses
        and legitimate ones.
        %We note there are several /64 subnets that had many
        %addresses that appeared random (visibly overlapping the random distribution).
    }
    \label{fig:ipbits}
\end{figure}
}
